Insect-venom elicited anaphylaxis: Data from the European Anaphylaxis Registry

### 2019-08-27 insect venom.Rmd
gramarly check

# Abstract
<!-- 350 Words unstructured -->
Insect-venom elicited anaphylaxis is a common and often severe hypersensitivity reaction. It affects older individuals than other anaphylaxis causes (p = `r t.test(data$d_age[data$d_elicitorInsect=="yes"],data$d_age[data$d_elicitorInsect=="no"])$p.val`). Using the data from the European Anaphylaxis Registry (`r v$allCases` cases in total) we identified insect-venom elicited anaphylaxis cases (n = `r v$insectElicited`) and analyzed these in comparison to anaphylaxis elicited by other elicitors (n = `r v$otherEli`).

>>>>

# Abstract
<!-- 350 Words unstructured -->
Insect-venom elicited anaphylaxis is a common and often severe hypersensitivity reaction. It affects older individuals than other anaphylaxis causes (p = `r t.test(data3$d_age[data3$d_elicitorInsect=="yes"],data$d_age[data$d_elicitorInsect=="no"])$p.val`). Using the data from the European Anaphylaxis Registry (`r v$allCases` cases in total) we identified insect-venom elicited anaphylaxis cases (n = `r v$insectElicited`) and analyzed these in comparison to anaphylaxis elicited by other elicitors (n = `r v$otherEli`).
